 \documentclass{article}
\usepackage[utf8]{inputenc}

\title{PS1}
\author{Joel Henriques}
\date{January 2020}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Introduction}
I took your econometric analysis course last Fall, and it was such an eye-opening experience to be able to effectively utilizes data to answer important questions. Data sciences seems to be a method to uncover the truths about the world without having to reply on others. I think there is something extremely profound, powerful, and absolutely fascinating about seeking truths in addition to answering unbelievably difficult questions with the help of data science. Economics is truly the primer for all of business. I use economics everyday in private equity in order to know which companies have the competitive advantage in their industry. 

I've enjoyed all of your classes and at the end of your econometric analysis course you basically said, "but wait there's more..." by stating that you'd be teaching a data science course for economists. So, obviously I had to sign up for the sequel. I have absolutely no idea what to research thus far, however, it will probably be in the realm of private equity/hedge fund analysis. My class goals are to have a pretty concrete understanding of data science and to further improve these skills for by applying to a data science masters. My plans after graduation is to either work as an investment banking analyst in California or take a different position in management consultant, where I would be utilizing my programming skills. Also, I hope to be accepted into an online data science masters program. 



\section{Equation}
$a^2+b^2=c^2$

\bibliographystyle{plain}

\end{document}
